Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-05-03 analysis/paper/paper.Rmd
Fix crossrefs

# table captions
tn <- local({
  i = 0
  function(x) {
    i <<- i + 1
    paste('\n\nTab. ', i, ': ', x, sep = '')
    # The : before Table tells pandoc to wrap your caption in <caption></caption>
  }
})
knitr::knit_hooks$set(tab.cap = function(before, options, envir) {
  if (!before)
    tn(options$tab.cap)
})
default_output_hook = knitr::knit_hooks$get("output")
knitr::knit_hooks$set(output = function(x, options) {
  if (is.null(options$tab.cap) == F)  
    x
  else
    default_output_hook(x,options)
})

@@

The split-plot treatment rates of N were N0 (no N supply), N100 (100 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) and N120 (120 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) (Tab. \@ref(tab:N-rates)).

@@

Split-plot N rates differed from the 2015 rates with only two N treatments, N60 (60 kg per ha as urea split into two applications) and N180 (180 kg per ha in three splits) being applied  (Tab. \@ref(tab:N-rates)).

@@

In 2015 the incidence of tiller ShB remained low throughout the growing season (Fig. \@ref(fig:ShB-W-progress)a, \@ref(fig:ShB-N-progress)a). Water management was not significantly different (Fig. \@ref(fig:ShB-W-box)a, \@ref(fig:estimates-plot)a). However, the N treatments, N100 and N120, were both significantly different when compared with the control N0 treatment (Fig. \@ref(fig:ShB-N-box)a, \@ref(fig:estimates-plot)a).

@@

Tiller ShB severity remained below 2% (Fig. \@ref(fig:ShB-N-progress)c, \@ref(fig:ShB-W-progress)c). Both the N100 and N120 treatments were significantly different than the control N0 treatment (Fig. \@ref(fig:ShB-N-box)c, \@ref(fig:estimates-plot)c). However, the AWD water management was not significantly different from the FLD treatment (Fig. \@ref(fig:ShB-W-box)c, \@ref(fig:estimates-plot)c).

@@

Severity of leaf ShB remained low, less than 0.4% across all treatments (Fig. \@ref(fig:ShB-W-progress)e, \@ref(fig:ShB-N-progress)e). Both the N100 and N120 treatments were significantly different than the N0 treatment (Fig. \@ref(fig:ShB-N-box)e, \@ref(fig:estimates-plot)e). However, the AWD water management was not significantly different from the FLD treatment (Fig. \@ref(fig:ShB-W-box)e, \@ref(fig:estimates-plot)e).

@@

The changes to the inoculation methodology resulted in a higher rate of infection in 2016, with the N180 treatment reaching a maximum value of 98% incidence at the third observation (Fig. \@ref(fig:ShB-N-progress)b). The N treatment N180, was significantly different than the control N60 treatment (Fig. \@ref(fig:ShB-N-box)b, \@ref(fig:estimates-plot)b). As in the 2015 study, water management did not significantly differ (Fig. \@ref(fig:ShB-W-box)b, \@ref(fig:estimates-plot)b).

@@

As with the tiller incidence, the tiller severity increased with the changed inoculation methods with a maximum of 7.6% for the flooded treatment (Fig. \@ref(fig:ShB-N-progress)d). 
In 2016 the N180 treatment was significantly different from the N60 treatment, with N180 severity being higher (Fig. \@ref(fig:ShB-N-box)d, \@ref(fig:estimates-plot)d). The AWD water management, which was lower than the FLD treatment, was also significantly different (Fig. \@ref(fig:ShB-W-box)d, \@ref(fig:estimates-plot)d).

@@

In 2016 the neither of the treatments, N rate or water management, were significantly different from the control treatments for leaf ShB severity (Fig. \@ref(fig:ShB-W-box)f, \@ref(fig:estimates-plot)f, \@ref(fig:ShB-N-box)f, \@ref(fig:estimates-plot)f).

@@

In both experiments we were unable to detect any significant effect of AWD on ShB that would cause increases in the disease, which could hinder adoption of the technology. In only one instance were we able to detect any effect of AWD on ShB. In the 2016 experiment the tiller ShB severity was significantly lower for AWD than FLD (Fig. \@ref(fig:ShB-W-box)d, \@ref(fig:estimates-plot)d), indicating a possible adverse effect of using AWD on tiller ShB severity under conditions where there is high sheath blight pressure.

@@

The changes made for the 2016 experiment appear to have improved the experiment, increasing the incidence and decreased variability of sheath blight in the plots (Fig. \@ref(fig:ShB-W-progress)a:b, \@ref(fig:ShB-N-progress)c:d, \@ref(fig:ShB-W-box)a:b, \@ref(fig:ShB-N-box)c:d). The rice establishment method is known to affect the spread of sheath blight [@Willocquet2000]. It is possible that the mechanical transplanter could increase ShB spread in the canopy as compared with traditional manual transplanting. This however was not investigated as a part of this study but could bear further research.

@@

# Tables {-}\

@@

`r figure_nums("fig_1")`
```{r ShB-W-progress, fig.cap="fig.1_cap"}

@@

##### ShB W progress
`r figure_nums("fig_2")`
```{r ShB-N-progress, fig.cap="fig.2_cap"}

@@

`r figure_nums("fig_3")`
```{r ShB-W-box, fig.cap="fig.3_cap"}

@@

##### ShB boxplot - NRTE
`r figure_nums("fig_4")`
```{r ShB-N-box, fig.cap="fig.4_cap"}

@@

##### Estimates plot
`r figure_nums("fig_5")`
```{r estimates-plot, fig.cap="fig.5_cap"}

>>>>

@@

The split-plot treatment rates of N were N0 (no N supply), N100 (100 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) and N120 (120 kg per ha applied as urea in three splits at final harrowing, active tillering and panicle initiation) (Tab. \@ref(tab:tab_1)).

@@

Split-plot N rates differed from the 2015 rates with only two N treatments, N60 (60 kg per ha as urea split into two applications) and N180 (180 kg per ha in three splits) being applied (Tab. \@ref(tab:tab_1)).

@@

In 2015 the incidence of tiller ShB remained low throughout the growing season (Fig. \@ref(fig:fig_1)a, \@ref(fig:fig_2)a). Water management was not significantly different (Fig. \@ref(fig:fig_3)a, \@ref(fig:fig_5)a). However, the N treatments, N100 and N120, were both significantly different when compared with the control N0 treatment (Fig. \@ref(fig:fig_4)a, \@ref(fig:fig_5)a).

@@

Tiller ShB severity remained below 2% (Fig. \@ref(fig:fig_2)c, \@ref(fig:fig_1)c). Both the N100 and N120 treatments were significantly different than the control N0 treatment (Fig. \@ref(fig:fig_4)c, \@ref(fig:fig_5)c). However, the AWD water management was not significantly different from the FLD treatment (Fig. \@ref(fig:fig_3)c, \@ref(fig:fig_5)c).

@@

Severity of leaf ShB remained low, less than 0.4% across all treatments (Fig. \@ref(fig:fig_1)e, \@ref(fig:fig_2)e). Both the N100 and N120 treatments were significantly different than the N0 treatment (Fig. \@ref(fig:fig_4)e, \@ref(fig:fig_5)e). However, the AWD water management was not significantly different from the FLD treatment (Fig. \@ref(fig:fig_3)e, \@ref(fig:fig_5)e).

@@

The changes to the inoculation methodology resulted in a higher rate of infection in 2016, with the N180 treatment reaching a maximum value of 98% incidence at the third observation (Fig. \@ref(fig:fig_2)b). The N treatment N180, was significantly different than the control N60 treatment (Fig. \@ref(fig:fig_4)b, \@ref(fig:fig_5)b). As in the 2015 study, water management did not significantly differ (Fig. \@ref(fig:fig_3)b, \@ref(fig:fig_5)b).

@@

As with the tiller incidence, the tiller severity increased with the changed inoculation methods with a maximum of 7.6% for the flooded treatment (Fig. \@ref(fig:fig_2)d). 
In 2016 the N180 treatment was significantly different from the N60 treatment, with N180 severity being higher (Fig. \@ref(fig:fig_4)d, \@ref(fig:fig_5)d). The AWD water management, which was lower than the FLD treatment, was also significantly different (Fig. \@ref(fig:fig_3)d, \@ref(fig:fig_5)d).

@@

In 2016 the neither of the treatments, N rate or water management, were significantly different from the control treatments for leaf ShB severity (Fig. \@ref(fig:fig_3)f, \@ref(fig:fig_5)f, \@ref(fig:fig_4)f, \@ref(fig:fig_5)f).

@@

In both experiments we were unable to detect any significant effect of AWD on ShB that would cause increases in the disease, which could hinder adoption of the technology. In only one instance were we able to detect any effect of AWD on ShB. In the 2016 experiment the tiller ShB severity was significantly lower for AWD than FLD (Fig. \@ref(fig:fig_3)d, \@ref(fig:fig_5)d), indicating a possible adverse effect of using AWD on tiller ShB severity under conditions where there is high sheath blight pressure.

@@

The changes made for the 2016 experiment appear to have improved the experiment, increasing the incidence and decreased variability of sheath blight in the plots (Fig. \@ref(fig:fig_1)a:b, \@ref(fig:fig_2)c:d, \@ref(fig:fig_3)a:b, \@ref(fig:fig_4)c:d). The rice establishment method is known to affect the spread of sheath blight [@Willocquet2000]. It is possible that the mechanical transplanter could increase ShB spread in the canopy as compared with traditional manual transplanting. This however was not investigated as a part of this study but could bear further research.

@@

# Tables {-}

@@

`r figure_nums("fig_1")`
```{r fig_1, fig.cap="fig.1_cap"}

@@

##### ShB N progress
`r figure_nums("fig_2")`
```{r fig_2, fig.cap="fig.2_cap"}

@@

`r figure_nums("fig_3")`
```{r fig_3, fig.cap="fig.3_cap"}

@@

##### ShB boxplot - NRTE
`r figure_nums("fig_4")`
```{r fig_4, fig.cap="fig.4_cap"}

@@

##### Estimates plot
`r figure_nums("fig_5")`
```{r fig_5, fig.cap="fig.5_cap"}
